\LARGE \bf ***

### 2020-09-09 icra-2021.tex
friday's countdown (aka preparing a stable version for internal review [2])

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}{Corollary}
\newtheorem{conj}{Conjecture}[section]
\newtheorem{defn}{Definition}[section]
\newtheorem{exmp}{Example}[section]
\newtheorem{rem}{Remark}

@@

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

To evaluate the energy spent due to trajectory and computations, let us consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$
\begin{equation}\label{eqq:6}
  f(t)=\sum_{n=0}^{r}{a_n\cos{\frac{nt}{\xi}}+b_n\sin{\frac{nt}{\xi}}},
\end{equation}
where $\xi\in\mathbb{R}$ is the characteristic time, and $a_n, b_n\in\mathbb{R}$ for $n\in\{0,\dotsc,r\}$ the Fourier series coefficients.

@@

\begin{thm}\label{thm:2.2}
  Consider a continuously differentiable function $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$ at a time instant $k\in\mathbb{Z}_{>0}$.
  Assume a mobile robot performs a periodic mission free to move in $\mathcal{P}$ defined in~(\ref{eqq:2}), and likewise Lemma~\ref{lem:2.1}, the model behaves ideally. 
  Then the instantaneous energy is a linear combination of the state
  \begin{equation}
    y_k=C\mathbf{q}_k=\sum_{n=0}^r{a_n},
  \end{equation}
  where $a_n\in\mathbf{q}_k$ are the $r+1$ state's components at $k$ with $r$ being a pre-assigned arbitrary order, and $C$ is described by Equation~(\ref{eqq:8}).
\end{thm}
\begin{proof}
  *\\
\end{proof}

@@

The mechanical and computational control actions, $\mathcal{C}$ and $\mathcal{M}$ defined in Equation~(\ref{eqq:12})~and~(\ref{eqq:14}), are incorporated in the system in Equation~(\ref{eqq:9b}) using the input matrix
\begin{equation}\begin{split}
  \mathbf{u}_k&=\left[\begin{array}{cc}
    g\left(\mathcal{C}_k\right) & \mathcal{M}_k
  \end{array}\right]^T,\\
  B&=\left[\begin{array}{ccccccc}
    1 & \vline & 0 & \cdots & 0\\\hline
    0 & \vline & 0 & \cdots & 0\\
    \vdots & \vline & \vdots & \ddots & \vdots\\
    0 & \vline & 0 & \cdots & 0
  \end{array}\right],
\end{split}
\end{equation}
where $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, and $B\in\mathbb{R}^{j\times l}$ is the input matrix from Equation~(\ref{eqq:7})~and~(\ref{eqq:9b}). Moreover, the first column in the first row of the input matrix is $1$, while all the other items are $0$. This adds the computational model component to the energy evolution in the system in Equation~(\ref{eqq:9b}). The energy due to the change of explicit trajectory equation parameters is not directly added to the system, which however will update the reading from the sensors in Equation~(\ref{eqq:11b}) and thus adjust the energy evolution accordingly.

>>>>

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{assm}[thm]{Assumption}
\newtheorem{cor}{Corollary}
\newtheorem{conj}{Conjecture}[section]
\newtheorem{defn}{Definition}[section]
\newtheorem{exmp}{Example}[section]
\newtheorem{rem}{Remark}

@@

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}

@@

To evaluate the energy spent due to trajectory and computations, we formalize the following realistic assumption introduced in Section~\ref{sec:intro}.
\begin{assm}\label{assm:2.1}
The mission the mobile robots perform is periodic, in the sense that it presents repetitive patterns.
\end{assm}

Let us consider a Fourier series $f:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$
\begin{equation}\label{eqq:6}
  f(t)=\sum_{n=0}^{r}{a_n\cos{\frac{nt}{\xi}}+b_n\sin{\frac{nt}{\xi}}},
\end{equation}
where $\xi\in\mathbb{R}$ is the characteristic time, and $a_n, b_n\in\mathbb{R}$ for $n\in\{0,\dotsc,r\}$ the Fourier series coefficients.

@@

\begin{thm}\label{thm:2.2}
  Consider a continuously differentiable function $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$ at a time instant $k\in\mathbb{Z}_{>0}$.
  Assume Assumption~\ref{assm:2.1} holds, the robots is free to move in $\mathcal{P}$ defined in~(\ref{eqq:2}), and likewise in Lemma~\ref{lem:2.1}, the model behaves ideally. 
  Then, the instantaneous energy consumption is a linear combination of the state
  \begin{equation}
    y_k=C\mathbf{q}_k=\sum_{n=0}^r{a_n},
  \end{equation}
  where $a_n\in\mathbf{q}_k$ are the $r+1$ state's components at $k$ with $r$ being a pre-assigned arbitrary order, and $C$ is described by Equation~(\ref{eqq:8}).
\end{thm}
\begin{proof}
  *\\
\end{proof}

@@

The mechanical and computational control actions, $\mathcal{C}$ and $\mathcal{M}$ defined in Equation~(\ref{eqq:12})~and~(\ref{eqq:14}), are incorporated in the system in Equation~(\ref{eqq:9b}) using the input matrix
\begin{equation}
  \mathbf{u}_k=\left[\begin{array}{c}
    g\left(\mathcal{C}_k\right) \\\hline \mathcal{M}_k
  \end{array}\right],\,\,\,
  B=\left[\begin{array}{ccccccc}
    1 & \vline & 0 & \cdots & 0\\\hline
    0 & \vline & 0 & \cdots & 0\\
    \vdots & \vline & \vdots & \ddots & \vdots\\
    0 & \vline & 0 & \cdots & 0
  \end{array}\right],
\end{equation}
where $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, and $B\in\mathbb{R}^{j\times l}$ is the input matrix from Equation~(\ref{eqq:7})~and~(\ref{eqq:9b}). Moreover, the first column in the first row of the input matrix is $1$, while all the other items are $0$. This adds the computational model component to the energy evolution in the system in Equation~(\ref{eqq:9b}). The energy due to the change of explicit trajectory equation parameters is not directly added to the system, which however will update the reading from the sensors in Equation~(\ref{eqq:11b}) and thus adjust the energy evolution accordingly.
